Micromechanism of Cold Deformation of Two Phase Polycrystalline Ti-Al Alloy with Void Defect

### 2018-11-17 draft/alexpub.tex
修改图片格式

In Fig. \ref{fig:model-creation}, voids with different size: 2\AA, 5\AA, 10\AA, 15\AA\ were placed  at $\alpha_2-\gamma$ phase boundary, inside $\gamma$ phase respectively. The strength of materials with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}. The existence of void have little impact on the elastic properties of the material, and the model without void defect has the best strength 5.3 GPa, the yield stress of model with void is smaller. Void at $\alpha_2$-$\gamma$ phase boundary  detracts the strength of  material most, and the void inside $\alpha_2$ phase  have less impact on the strength.          
Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated by
\begin{equation} \label{eq:section} 
\sigma^* = \sigma_0 \cdot \frac{A^*}{A_0}
\end{equation}
where $\sigma_0$ is the strength of model without void defects 5.26 Gpa, and $A_0$ is initial section area,  $A^*$ is effective section area.  In classic theory, the relationship between void size and strength of the model is linear. However, simulation results reveals that two phase Ti-Al alloy is sensitive to existence of void defect.  Comparing with the strength determined by molecular dynamics simulation and the result4s calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects should be examined carefully.

>>>>

In Fig. \ref{fig:model-creation}, voids with different size: 2\AA, 5\AA, 10\AA, 15\AA\ were placed  at $\alpha_2$/$\gamma$ phase boundary, inside $\gamma$ phase respectively. The strength of materials with void in different size and at different position is shown in Fig.\ref{fig:stress&strain}. The existence of void have little impact on the elastic properties of the material, and the model without void defect has the best strength 5.3 GPa, the yield stress of model with void is smaller. Void at $\alpha_2$-$\gamma$ phase boundary  detracts the strength of  material most, and the void inside $\alpha_2$ phase  have less impact on the strength.          
Conventional definition of strength of materials with geometry subtraction was applied to the model, and theoretical strength of the models was calculated by
\begin{equation} \label{eq:section} 
\sigma^* = \sigma_0 \cdot \frac{A^*}{A_0}
\end{equation}
where $\sigma_0$ is the strength of model without void defects 5.26 Gpa, and $A_0$ is initial section area,  $A^*$ is effective section area.  In classic theory, the relationship between void size and strength of the model is linear. However, simulation results reveals that two phase Ti-Al alloy is sensitive to existence of void defect.  Comparing with the strength determined by molecular dynamics simulation and the result4s calculated with formulation \ref{eq:section}, it can be assumed that the main factor that affects the strength of materials can be attributed to local behavior of the materials, thus revolution of defects should be examined carefully.
